The Private School Network

### 2024-02-24 index.qmd
close #17

### One-mode percent matrix, all universities {.caption}

::: {.table-wrapper .tbl-1mode}
```{r pubu-privu-1mode}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df, align = 'r', escape = F) %>%
  column_spec(1, bold = T) %>% 
  column_spec(2:30, width_min = '0.9in')
```
:::

>>>>

### One-mode count matrix, all universities {.caption}

::: {.table-wrapper .tbl-1mode}
```{r pubu-privu-1mode}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_df) <- colnames(table_1mode_u$onemode_df)

names(table_1mode_u$onemode_df) <- str_replace(names(table_1mode_u$onemode_df), ' \\(', '<br>(')

kable(table_1mode_u$onemode_df, align = 'r', escape = F) %>%
  column_spec(1, bold = T) %>% 
  column_spec(2:30, width_min = '0.9in')
```
:::
